---
title: "fake report"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Load in `ggplot2`
library(ggplot2)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r}
data(fake2_2)
head(fake2_2)
str(fake2_2)
summary(fake2_2)
summary(fake2_2$type)
```

## Including Plots

You can also embed plots, for example:

```{r, echo=FALSE}
plot(fake2_2)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
```{r fake}
#Number of likes per country
country_likes<-aggregate(fake2_2$likes, by=fake2_2["country"], FUN=sum)
```
```{r}
#Number of bias per country
country_bias<-aggregate(fake2_2$type, by=fake2_2["country"], FUN=length)
country_bias<-aggregate(fake2_2$type=='bias', by=fake2_2["country"], FUN=length)
```
```{r}
# select bias only for like=1
like <- fake2_2[fake2_2$likes!=0,]
# number of countries likes recorded for tweet
unique(like$country)
# Number of bias if tweet liked for country
country_bias_liked<-aggregate(like$type, by=like["country"], FUN=length)
# assign name to column
country_bias_liked<- merge(country_bias_liked, country_codes, by.x="country", by.y = "CODES")
names(country_bias_liked)[2]<-'Number of Bias w/ Likes'
country_bias_liked
```
```{r}
#Number of bias per country by type
fake3<-unique(fake2_2$type)
country_bias_by_type<-aggregate(fake2_2$type, by=fake2_2["country"], FUN= subset(fake2_2, type == 'bias', select = type))
subset(fake2_2, type == 'bias', select = type)
country_bias[,'bias']<- length((fake2_2$type=='bias'))
```
```{r}
#Bias category per country
bias <- fake2_2[fake2_2$type=='bias',]
#number of bias news tweets per country
country_bias_bias<-aggregate(bias$type, by=bias["country"], FUN=length)
names(country_bias_bias)[2]<- 'bias_cat'
#merge(country_bias_bias, country_codes, by.x="country", by.y = "CODES")
```
```{r}
#Bs category per country
bs <- fake2_2[fake2_2$type=='bs',]
#number of bs news tweets per country
country_bias_bs<-aggregate(bs$type, by=bs["country"], FUN=length)
names(country_bias_bs)[2]<- 'bs_cat'
#Merge above table
country_bias_bs<-merge(country_bias_bias, country_bias_bs, by.x="country", by.y = "country", all = TRUE)
```
```{r}
#Conspiracy category per country
con <- fake2_2[fake2_2$type=='conspiracy',]
#number of bs news tweets per country
country_bias_con<-aggregate(con$type, by=con["country"], FUN=length)
names(country_bias_con)[2]<- 'con_cat'
#Merge above table
country_bias_con<-merge(country_bias_bs, country_bias_con, by.x="country", by.y = "country", all = TRUE)
```
```{r}
#Fake category per country
fake <- fake2_2[fake2_2$type=='fake',]
#number of bs news tweets per country
country_bias_fake<-aggregate(fake$type, by=fake["country"], FUN=length)
names(country_bias_fake)[2]<- 'fake_cat'
#Merge above table
country_bias_fake<-merge(country_bias_con, country_bias_fake, by.x="country", by.y = "country", all = TRUE)
```
```{r}
#Hate category per country
hate <- fake2_2[fake2_2$type=='hate',]
#number of bs news tweets per country
country_bias_hate<-aggregate(hate$type, by=hate["country"], FUN=length)
names(country_bias_hate)[2]<- 'hate_cat'
#Merge above table
country_bias_hate<-merge(country_bias_fake, country_bias_hate, by.x="country", by.y = "country", all = TRUE)
```
```{r}
#Junksci category per country
junksci <- fake2_2[fake2_2$type=='junksci',]
#number of junksci news tweets per country
country_bias_junksci<-aggregate(junksci$type, by=junksci["country"], FUN=length)
names(country_bias_junksci)[2]<- 'junksci_cat'
#Merge above table
country_bias_junksci<-merge(country_bias_hate, country_bias_junksci, by.x="country", by.y = "country", all = TRUE)
```
```{r}
#Satire category per country
satire <- fake2_2[fake2_2$type=='satire',]
#number of satire news tweets per country
country_bias_satire<-aggregate(satire$type, by=satire["country"], FUN=length)
names(country_bias_satire)[2]<- 'satire_cat'
#Merge above table
country_bias_satire<-merge(country_bias_junksci, country_bias_satire, by.x="country", by.y = "country", all = TRUE)
```
```{r}
#State category per country
state <- fake2_2[fake2_2$type=='state',]
#number of state news tweets per country
country_bias_state<-aggregate(state$type, by=state["country"], FUN=length)
names(country_bias_state)[2]<- 'state_cat'
country_bias_state<-merge(country_bias_satire, country_bias_state, by.x="country", by.y = "country", all = TRUE)
country_bias_total<-merge(country_bias_state, country_codes, by.x="country", by.y = "CODES")
```
```{r}
#Number of likes per countries w/ bias
country_bias_liked_liked<-merge(country_bias_state,country_bias_liked, by.x="country", by.y = "country", all = TRUE)
country_bias_liked_liked<-merge(country_bias_liked_liked, country_codes, by.x="country", by.y = "CODES")
```
```{r}
#Number of likes per type
# select bias only for like>1
like <- fake2_2[fake2_2$likes!=0,]
# number of countries likes recorded for tweet
unique(like$country)
# Number of likes per type
bias_liked<-aggregate(like$likes, by=like["type"], FUN=length)
```
```{r}
# Number of likes per site with likes
site_likes<-aggregate(like$likes, by=like["site_url"], FUN=sum)
site_likes_all<-aggregate(fake2_2$likes, by=fake2_2["site_url"], FUN=sum)
```


#Same as above for urls

```{r}
#Bias category per country
bias <- fake2_2[fake2_2$type=='bias',]
#number of bias news tweets per country
url_bias_bias<-aggregate(bias$type, by=bias["site_url"], FUN=length)
names(url_bias_bias)[2]<- 'bias_cat'
#merge(country_bias_bias, country_codes, by.x="country", by.y = "CODES")
```
```{r}
#Bs category per country
bs <- fake2_2[fake2_2$type=='bs',]
#number of bs news tweets per country
url_bias_bs<-aggregate(bs$type, by=bs["site_url"], FUN=length)
names(url_bias_bs)[2]<- 'bs_cat'
#Merge above table
url_bias_bs<-merge(url_bias_bias, url_bias_bs, by.x="site_url", by.y = "site_url", all = TRUE)
```
```{r}
#Conspiracy category per country
con <- fake2_2[fake2_2$type=='conspiracy',]
#number of bs news tweets per country
url_bias_con<-aggregate(con$type, by=con["site_url"], FUN=length)
names(url_bias_con)[2]<- 'con_cat'
#Merge above table
url_bias_con<-merge(url_bias_bs,url_bias_con, by.x="site_url", by.y = "site_url", all = TRUE)
```
```{r}
#Fake category per country
fake <- fake2_2[fake2_2$type=='fake',]
#number of bs news tweets per country
url_bias_fake<-aggregate(fake$type, by=fake["site_url"], FUN=length)
names(url_bias_fake)[2]<- 'fake_cat'
#Merge above table
url_bias_fake<-merge(url_bias_con,url_bias_fake, by.x="site_url", by.y = "site_url", all = TRUE)
```
```{r }
#Hate category per country
hate <- fake2_2[fake2_2$type=='hate',]
#number of bs news tweets per country
url_bias_hate<-aggregate(hate$type, by=hate["site_url"], FUN=length)
names(url_bias_hate)[2]<- 'hate_cat'
#Merge above table
url_bias_hate<-merge(url_bias_fake, url_bias_hate, by.x="site_url", by.y = "site_url", all = TRUE)
```
```{r}
#Junksci category per country
junksci <- fake2_2[fake2_2$type=='junksci',]
#number of junksci news tweets per country
url_bias_junksci<-aggregate(junksci$type, by=junksci["site_url"], FUN=length)
names(url_bias_junksci)[2]<- 'junksci_cat'
#Merge above table
url_bias_junksci<-merge(url_bias_hate, url_bias_junksci, by.x="site_url", by.y = "site_url", all = TRUE)
```
```{r}
#Satire category per country
satire <- fake2_2[fake2_2$type=='satire',]
#number of satire news tweets per country
url_bias_satire<-aggregate(satire$type, by=satire["site_url"], FUN=length)
names(url_bias_satire)[2]<- 'satire_cat'
#Merge above table
url_bias_satire<-merge(url_bias_junksci, url_bias_satire, by.x="site_url", by.y = "site_url", all = TRUE)
```
```{r}
#State category per country
state <- fake2_2[fake2_2$type=='state',]
#number of state news tweets per country
url_bias_state<-aggregate(state$type, by=state["site_url"], FUN=length)
names(url_bias_state)[2]<- 'state_cat'
url_bias_state<-merge(url_bias_satire, url_bias_state, by.x="site_url", by.y = "site_url", all = TRUE)
```
```{r}
#Number of likes per countries w/ bias
country_bias_liked_liked<-merge(country_bias_state,country_bias_liked, by.x="country", by.y = "country", all = TRUE)
country_bias_liked_liked<-merge(country_bias_liked_liked, country_codes, by.x="country", by.y = "CODES")
```

